---
title: "Group_07_Analysis"
author: "Boyang Sun,Lina Zhou,Yitong Liu,Yifan Kong,Zhengliang Zhang"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE, comment = NA,tidy.opts=list(width.cutoff=55),tidy=TRUE)
```


```{r libraries}
#import following libraries
library(ggplot2)
library(tidyverse)
library(dplyr)
library(GGally)
library(readr)
library(kableExtra)
library(gridExtra)
library(formatR)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
```

# Introduction {#sec:intro}

The IMDB rating is a contextual concern for filmmakers because it reflects the quality and popularity of a movie. the IMDB rating can be used as an indicator for filmmakers to review the content of a movie. It can help them determine whether the movie is likely to be a huge success and whether the movie is likely to be well received by audiences. In addition, IMDB ratings can help filmmakers evaluate the economics of a film to determine if it is worth investing in.Based on this background, this report explores this main issue below to serve filmmakers.

Question:
**Which properties of films influence whether they are rated by IMDB as greater than 7 or not? ** 

By studying the factors that influence IMDB, it can help filmmakers make more accurate judgments.

```{r data, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}

#Data pre-processing

#Set the current working directory
setwd("/Users/zhoulina/DAS-Group-07")

#Read data
film<-read_csv("dataset7.csv")

#Data cleansing

#Add categorical variables goodtype and goodtype_flag
film<-film%>%
  mutate( 'goodtype'= ifelse(rating> 7,'greater than 7', 'less than 7'))%>%
  mutate( 'goodtype_flag'= ifelse(rating> 7,1,0))


#Remove invalid data rows with null values
film<- na.omit(film)


#Select the fields available for analysis based on business implications,Exclude vote and film.id

film_data<-film%>%
      select('year','length','budget','genre','rating','goodtype','goodtype_flag')
```

# Exploratory data analysis {#sec:eda}

## Variable Description


***year*** Year of release of the film in cinemas

***length***  Duration (in minutes)

***budget*** Budget for the films production (in $1000000s)

***genre*** Genre of the film

***rating*** IMDB rating from 0-10

***goodtype*** IMDB rating greater than 7 description

***goodtype_flag*** IMDB rating greater than 7 then 1 else 0


These are the explanatory notes for each field of the dataset.


## Data Summary

The following table shows all the variables to be explored for this dataset.

\newpage
```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#Data table display after data cleaning

kable(head(film_data, n = 10), 
      caption = '\\label{tab:film_data} The first 10 
      rows of the film data.')%>%
  kable_styling(font_size = 7, latex_options = 'h')
```

Table 1 contains 7 columns of data, and the question of our research revolve around  ***goodtype_flag*** as the response variable,numerical explanatory variables: ***year***,***length***,***budget***, and a categorical explanatory variable ***genre*** to develop the corresponding exploration.


```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#Produce a data summary of the response variable goodtype_flag

film_data%>%
  group_by(goodtype)%>%
  summarise(n=n())%>%
  kable(caption = '\\label{tab:film_data} table of the type of IMDB')%>%
  kable_styling(latex_options = "hold_position")
```



Table 2 contains summary statistics on the type of IMDB. There are `r nrow(film_data)` observations. We can see that IMDB ***greater than 7*** has `r nrow(film_data[film_data$goodtype == 'greater than 7', ])` observations and
 IMDB ***less than 7*** has `r nrow(film_data[film_data$goodtype == 'less than 7', ])` observations.
 
 
## Data visualization display

```{r, eval = TRUE, out.width = '50%', fig.align = "center",warning = FALSE, fig.cap = '\\label{fig:film_data} The length by the type of IMDB'}
#Plotting length under different goodtype

ggplot(data = film_data, aes(x =goodtype, y = length,fill = goodtype)) +
  geom_boxplot() +
  labs(x = "goodtype", y = "length")+ 
  theme(legend.position = "none")

```


The boxplot in Figure 1 shows that the distribution of variable length in each goodtype.We can find that the length of most films with rate greater than 7 is shorter than the films with rate less than 7, and the distribution of the length of the films with rate less than 7 centralized around its median with small variability.

\newpage
```{r, eval = TRUE, out.width = '60%', fig.align = "center",warning = FALSE, fig.cap = '\\label{fig:film_data} budget and year by the type of IMDB'}
#Plotting length under different goodtype 

p1<-ggplot(data = film_data, aes(x =goodtype, y = budget,fill = goodtype)) +
  geom_boxplot() +
  labs(x = "goodtype", y = "budget")+ 
  theme(legend.position = "none")

#Plotting length under different goodtype 

p2<-ggplot(data = film_data, aes(x =goodtype, y = year,fill = goodtype)) +
  geom_boxplot() +
  labs(x = "goodtype", y = "year")+ 
  theme(legend.position = "none")
grid.arrange(p1,p2,nrow=1,widths=c(4,4))
```


The boxplots in Figure 2 above show that the difference between the distribution of the variables ***budget*** and ***year*** in each goodtype is small.


## Correlation matrix

Besides of the boxplot, the correlation coefficient between variables also need to be checked.

```{r, eval = TRUE, out.width = '60%', fig.align = "center",warning = FALSE, fig.cap = '\\label{fig:film_data} The correlation coefficient between variables.'}
#Check the correlation coefficient between variables

ggpairs(film_data[c("year","length","budget")])
```
\newpage

The correlations between the variables are all less than 0.16 which is quite low. It seems there does not have the question of collinearity.

Moreover, the categorical variable genre may also have an influence in the prediction of the response variable goodtype_flag. Thus, check the proportion of different genres under each goodtype, which shows below:

```{r, eval = TRUE, out.width = '70%', fig.align = "center",warning = FALSE, fig.cap = '\\label{fig:film_data} The proportion of different genres under each type of IMBD'}
ggplot(film_data, aes(x= goodtype,  y = ..prop.., group=genre, fill=genre)) + 
    geom_bar(position="dodge", stat="count") +
    labs(y = "Proportion")
```

It is obvious that considering the categorical variable genre in the prediction of goodtype will make sense.



# Formal data analysis



Before formal analysis, check the type of the variables and confirm everything is ready for the model fitting. 
```{r, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
str(film_data)
```

## Model Fit

```{r model1,echo=TRUE,eval=TRUE,warning=FALSE,message=FALSE}
# the first GLM named model1

model1 <- glm(goodtype_flag ~ year + length + budget + genre, data = film_data, family = binomial(link = "logit"))

# summary of model1

summ(model1)
```
\newpage
It can be observed that the p-value of the variable *year* is larger than 0.05, which indicates that *year* does not have a significant relationship with the response variable. Thus, we remove it and fit the new model again.

## New Model Fit 

```{r model2, echo=TRUE,eval=TRUE,warning=FALSE,message=FALSE}
# the new GLM named model2

model2 <- glm(goodtype_flag ~ length + budget + genre, 
               data = film_data, family = binomial)

# summary of model2

summ(model2)
```
\newpage
As shown above, the p-values of all variables are less than 0.05. Therefore, we will use this model to conduct the prediction and analysis.
From the result, we can get the values of all coefficients. For example, $\beta_1 =$ -0.05, which means the log-odds of the film rating greater than 7 decrease by 0.05 for one unit increase in *length*.

## Log-Odds Ratio

Besides of the point estimates of the coefficients shown above, we can also get the 95% Confidence Intervals for each variable of model2.

```{r , echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
# Computing the confidence intervals for each variable of model2

confint(model2) %>%
  kable(align = "c", digits = 2, booktabs = TRUE)%>%
  kable_styling(font_size = 10, latex_options = 'h')
```

The following shows the plot of the 95% Confidence Intervals:
```{r , echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
# Plotting the confidence intervals of coefficients

plot_model(model2, show.values = TRUE, transform = NULL,
           title = "The influence of predictors on the rating of movies",
           show.p = FALSE,) + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Variables", y = "Log-odds ratio")
```

We interpret the log-odds ratios as follows:

* For every minute increase in the movies' *length*, their log-odds of getting rating greater than 7 decrease(by a factor of **0.97**).

* For every million dollars' increase in *budget*, their log-odds of obtain rating than 7 increase(by a factor of **0.5**)

* When the movie genres are *Comedy*, *Documentary*, and *Short*, the log-odds of their rating being above **7** are **2.75**, **4.8**, and **4.24** times higher than the movie genre *Action*.

* When the movie genres are *Animation*, *Drama*, and *Romance*, the log-odds of their rating being below 7 is **0.15**, **2.04**, and **13.63** times higher than the movie genre *Action*.

We can also get the estimates of the log-odds of the fitted model:

```{r,echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#compute the estimates of the log-odds

film_data<-film_data%>%
  mutate(logodds.goodtype = predict(model2))
kable(head(film_data, n = 10),
      caption = '\\label{tab:filmdata} The first 10 rows of 
      the film data with log-odds',align = "c") %>% 
  kable_styling(font_size = 9, latex_options = 'h')
```


## Odds

The formula is as follows:

\begin{align}
\frac{p}{1-p}\ &= exp(\alpha+ \beta_1 \cdot \textrm{Length}+\beta_2 \cdot \textrm{Budget}+\beta_3 \cdot I_{Animation}+\beta_4 \cdot I_{Comedy} +\nonumber \\
&\beta_5 \cdot I_{Documentary}+\beta_6 \cdot I_{Drama}+\beta_7 \cdot I_{Romance}+\beta_8 \cdot I_{Short}\nonumber)
\end{align}
in which $p$ represents the probability of the film rating greater than 7

Thus, we can get the estimates of the odds from the log-odds:

```{r exp_log_odds, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
# Indexation of the probability estimates
model2 %>%
  coef() %>%
  exp()
```

```{r,echo = TRUE, eval = TRUE,  out.width = '80%', fig.align = "center", warning = FALSE,  fig.pos="H",fig.cap = '\\label{fig:rate} The odds for different variables.'}

#Plotting confidence intervals

plot_model(model2, show.values = TRUE,
           title = "Odds (Film rating greater than 7)", show.p = FALSE)

```

On the odds scale, we can conclude that:

* For *length*, we have an odds ratio of **0.95**, which suggests that for every 1 Unit increase in *length*, the odds ratio for a movie with a rating greater than 7 increases by a factor of 0.95. 

* For *budget*, we have an odds ratio of **1.64**, which indicates that for every 1 unit increase in *budget*,
the odds ratio for a movie with a rating greater than 7 increase by a factor of 1.64.

* For *genre*, the odds of movies with a rating greater than 7 given their genre of *Animation* are **0.86** times greater than their genre of *Action*.

* For *genre*, the odds of movies with a rating greater than 7 given their genre of *Comedy* are **15.62** times greater than their genre of *Action*.

* For *genre*, the odds of movies with a rating greater than 7 given their genre of *Documentary* are **122** times greater than their genre of *Action*.

* For *genre*, the odds of movies with a rating greater than 7 given their genre of *Drama* are **0.13** times greater than their genre of *Action*.

* For *genre*, the odds of movies with a rating greater than 7 given their genre of *Romance* are the same with their genre of *Action*.

* For *genre*, the odds of movies with a rating greater than 7 given their genre of *Short* are **69.22** times greater than their genre of *Action*.


```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#compute estimates of the odds from lof-odds

film_data<-film_data%>%
  mutate(odds.goodtype = exp(logodds.goodtype))
kable(head(film_data, n = 10), 
      caption = '\\label{tab:filmdata} The first 10 rows of 
      the film data with odds',
      align = "c") %>%  
  kable_styling(font_size = 7, latex_options = 'h')
```

## Probability

Based on the estimates of the odds we got above, we can compute $p$

```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
#compute the value of p

film_data<-film_data%>%
  mutate(p=fitted(model2))
kable(head(film_data, n = 10),
      caption = '\\label{tab:filmdata} The first 10 rows of 
      the film data with p',align = "c")%>%
  kable_styling(font_size = 7, latex_options = 'h')
```


```{r, echo = TRUE,eval = TRUE,  out.width = '70%',fig.align = "center",warning = FALSE,fig.pos="H",fig.cap = '\\label{fig:rate} Comparing predictions and observations.'}
#Graphical display of the model

plot_model(model2,type = "pred",
           title = "Prob. of the rating of the film greater than 7")
```

The regression model of movie length on the probability of a film rating greater than 7 clearly shows that:
Overall, the probability of a movie rating greater than 7 decreases as the length of the movie increases

* In the range of 0 to 60 minutes, the decrease is the greatest

* In the range of 60 to 100, the decline slows down

* Above 100 minutes, the basic probability is 0 and does not change


The regression model of budget on the probability of a movie rating greater than 7 clearly shows that:

Overall, the probability of a movie rating greater than 7 increases gradually as the movie budget increases, but above 20, the growth slows down.

* In the range from 0 to 5, the probability of a movie rating greater than 7 increases essentially no more as the budget increases

* In the range from 5 to 10, the probability of a movie rating greater than 7 increases slightly

* In the range of 10-20, the probability of a movie rating greater than 7 increases significantly with an increasing budget

* In the range of 20 and above, the probability of a movie rating greater than 7 increases with budget, but the rate of increase slows

The regression model of genre and the probability of a film rating greater than 7 clearly shows that.

* Films belonging to the "Drama", "Action", "Animation" and "Romance" genres always have a low probability of rating higher than 7.

* Films belonging to the "Documentary", "Comedy" and "Short" genres always have a high probability of rating greater than 7.

* Films in the "Short" genre have a highly swinging probability of rating greater than 7.

## Conclusion

***Length, budget, and genre are three properties that affect whether a film is rated greater than 7 by IMDB***



